single_elimination

### 2025-10-22 CMSAC_presentation/CMSAC_reveal_js.qmd
Updates

@@

-   **Efficacy**[^1]: Final rankings should match the true rankings of all the competitors

@@

::: {.fragment}
-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Effectivity: 1 is only salient rank
    -   Efficacy: 1 through $n$ are salient ranks
:::

@@

-   Want to quantify how well a structure can accurately order the competitors
-   We propose a metric that quantifies how effectively different tournament structures recover the true ranking

@@

::: notes
If one views the true ranking of the teams in a tournament as a message to be sent to a receiver and the outcome of the tournament as a message that is received, we can measure the "goodness" of a tournament in terms of its ability to accurately transmit the true ranking.
:::

@@

    $$ I(r, \hat{r}) = n! \sum_{\hat{r}} p(r, \hat{r}) \log{\frac{p(r,\hat{r})}{(\frac{1}{n!})^2}} = n! \log{((n!)^2)} $$

@@

-   A limitation of mutual information is that it does not distinguish between the direction of information
-   In other words, given equal probabilities, a ranking of $(1,2,3,4)$ is equivalent to $(4,3,2,1)$
-   Because of this, we proposed a new weighting function\
    $$ wI_m(r,\hat{r}) = \sum_r \sum_{\hat{r}} w(r,\hat{r}) * p(r, \hat{r}) \log{\frac{p(r,\hat{r})}{p(r)p(\hat{r})}} $$
-   The final metric we used normalizes the results: $\frac{wI_m(r,\hat{r})}{H(r,\hat{r})}$

## Weighting Function

-   In our original paper submission, we used squared error loss as the weighting function: $w(r, \hat{r}) = \begin{cases} \frac{1}{(r-\hat{r})^2}, & r \neq \hat{r} \\ 1, & r = \hat{r} \end{cases}$
-   However, after comments and reviews from people at CSAS and CMSAC, we have decided to use a weighted Kendall's Tau

@@

```{r}
# Get the filtered data
table_data <- rhat_df %>% 
  select(-squared_error) %>%   
  filter(permutation %in% c("1234", "4321", "1324", "2143")) %>%   
  arrange(permutation, k) %>%   
  rename("Weighted Kendall" = weighted_kendall)

# Split into two halves
n <- nrow(table_data)
left_table <- table_data %>% head(ceiling(n/2))
right_table <- table_data %>% tail(floor(n/2))

# Create side-by-side tables
left_html <- left_table %>% 
  kable(format = "html", row.names = FALSE) %>% 
  kableExtra::kable_styling(font_size = 24)

right_html <- right_table %>% 
  kable(format = "html", row.names = FALSE) %>% 
  kableExtra::kable_styling(font_size = 24)
```

::::: columns
::: {.column width="48%"}
```{r}
#| echo: false
left_html
```
:::

::: {.column width="%48%"}
```{r}
#| echo: false
right_html
```
:::
:::::

$$ \tau_w = \frac{\sum_{i\neq j} W_{ij} \text{ sgn}(i-j) \text{ sgn}(R_i - R_j)}{\sum_{i,j} W_{ij} - \sum_i W_{ii}}$$

@@

-   Given the assigned "known strength", $\theta$, we simulate a game using the Bradley-Terry Model: $\Pr(i > j) = \frac{e^{\theta_i}}{e^{\theta_i} + e^{\theta_j}} = \frac{1}{1+e^{\theta_i - \theta_j}}$
-   Below is an example of the output of a single tournament simulation:

```{r}
renamed_df <- all_results_norm %>%    
  select(-c(simulation, distribution, seed, teams)) %>%   
  rename(theta = true_strength, r = true_rank, r_hat = rank_hat, "Wins" = game_wins, "Losses" = game_losses) %>%   
  mutate(theta = round(theta,3)) %>%
  head(8)

# Split into two halves
n <- nrow(renamed_df)
left_table <- renamed_df %>% head(ceiling(n/2))
right_table <- renamed_df %>% tail(floor(n/2))

# Create side-by-side tables
left_html <- left_table %>% 
  kable(format = "html", row.names = FALSE) %>% 
  kableExtra::kable_styling(font_size = 24)
right_html <- right_table %>% 
  kable(format = "html", row.names = FALSE) %>% 
  kableExtra::kable_styling(font_size = 24)

@@

::::: columns
::: {.column width="48%"}
```{r}
#| echo: false
left_html
```
:::

::: {.column width="%48%"}
```{r}
#| echo: false
right_html
```
:::
:::::

@@

## Conclusion

-   These results underscore the trade-off between tournament accuracy and practical constraints such as time, cost, and entertainment value.
-   Limitations: The "known" strengths are assumptions that can be estimated but never truly known
-   Future Work: Estimate the $\theta$s in a real-world example and compare recent changes to the old format

>>>>

-   **Efficacy**: Final rankings should match the true rankings of the strength of the competitors

-   **Effectivity**: Interested in correctly ranking the best competitor as first
:::

@@

-   **Efficacy**[^1]: Final rankings should match the true rankings of the strength of the competitors

@@

::: {.fragment}
-   **Salient ranks**: output ranks of the competition you want to get correct
    -   Effectivity: 1 is only salient rank
    -   Efficacy: 1 through $n$ are salient ranks
:::

@@

-   Want to quantify how well a structure can accurately order the competitors
-   We propose a metric that quantifies how effectively different competition structures recover the true ranking

@@

::: notes
If one views the true ranking of the teams in a competition as a message to be sent to a receiver and the outcome of the competition as a message that is received, we can measure the "goodness" of a competition in terms of its ability to accurately transmit the true ranking.
:::

@@

    $$ I(r, \hat{r}) = n! \sum_{\hat{r}} p(r, \hat{r}) \log{\frac{p(r,\hat{r})}{(\frac{1}{n!})^2}} $$

@@

-   A limitation of mutual information is that it does not distinguish between the direction of information
-   Given equal probabilities, the information found from a ranking of $(1,2,3,4)$ is equivalent to $(4,3,2,1)$
-   Because of this, we proposed a new weighting function\
    $$ I_w(r,\hat{r}) = \sum_r \sum_{\hat{r}} w(r,\hat{r}) * p(r, \hat{r}) \log{\frac{p(r,\hat{r})}{p(r)p(\hat{r})}} $$
-   The final metric we used normalizes the results: $\frac{I_w(r,\hat{r})}{H(r,\hat{r})}$

@@

```{r}
# Get the filtered data
#table_data <- rhat_df %>% 
#  select(-squared_error) %>%   
#  filter(permutation %in% c("1234", "4321", "1324", "2143")) %>%   
#  arrange(permutation, k) %>%   
#  rename("Weighted Kendall" = weighted_kendall)

# Split into two halves
#n <- nrow(table_data)
#left_table <- table_data %>% head(ceiling(n/2))
#right_table <- table_data %>% tail(floor(n/2))

# Create side-by-side tables
#left_html <- left_table %>% 
#  kable(format = "html", row.names = FALSE) %>% 
#  kableExtra::kable_styling(font_size = 24)

#right_html <- right_table %>% 
#  kable(format = "html", row.names = FALSE) %>% 
#  kableExtra::kable_styling(font_size = 24)
knitr::include_graphics("Top_k_Kendall.png")

@@

-   Given the assigned "known strength", $\theta$, we simulate a game using: $\Pr(i > j) = \frac{e^{\theta_i}}{e^{\theta_i} + e^{\theta_j}} = \frac{1}{1+e^{\theta_i - \theta_j}}$

```{r}
renamed_df <- single_run_example %>%    
  select(-c(distribution, seed)) %>%   
  rename(theta = true_strength, r = true_rank, r_hat = rank_hat, "Wins" = game_wins, "Losses" = game_losses) %>%   
  mutate(theta = round(theta,3))

# Create side-by-side tables
html_df <- renamed_df %>% 
  kable(format = "html", row.names = FALSE) %>% 
  kableExtra::kable_styling(font_size = 24)

@@

::::: columns
::: {.column width="48%"}
```{r}
#| echo: false
html_df
```
:::

::: {.column width="%48%"}
```{r}
#| echo: false
#| out.width: "100%"
knitr::include_graphics("simulation_example.png")
```
:::
:::::

@@

## Discussion

-   We used mutual information to analyze competition structures in a range from efficacy to effectivity.
-   Using the method, we found that Round Robin is the best structure, followed by Reseeded Single Elimination, Double Elimination, and Group Stage.
-   Limitations: The "known" ranks are assigned using $\theta$ and, for some structure, the order of the ranks matter in the formatting of the structure
-   Future Work: Examine how the distribution of $\theta$s influence the score of each competition structure

### 2025-10-22 mutual_information_curves.qmd
Updates

# Reshape data into long format for ggplot
df_long <- pivot_longer(mi_plots_df, cols = -indices, names_to = "Method", values_to = "MI")

okabe_ito <- c(
  "#E69F00", # orange
  "#56B4E9", # sky blue
  "#009E73", # bluish green
  "#F0E442", # yellow
  "#0072B2", # blue
  "#D55E00", # vermillion
  "#CC79A7", # reddish purple
  "#999999", # gray
  "#8A2BE2", # violet (extra)
  "#20B2AA"  # teal (extra)
)
# Define consistent color mapping
methods <- unique(df_long$Method)
method_colors <- setNames(okabe_ito, methods)

windowsFonts(Arial = windowsFont("Arial"))
ggplot(df_long, aes(x = indices, y = MI, color = Method, group = Method)) +
geom_line(linewidth = 2.5) +           # Add lines
geom_point(size=3) +          # Add points
labs(
title = "Comparison of Tournament Structures with Normal Strengths",
x = "Top i Number of Teams",
y = "Normalized Mutual Information \\ Entropy (log10 scale)"
) +
theme_minimal() +       # Use a clean theme
theme(text = element_text(family = "Arial", size = 32),
  legend.position = "bottom",
  legend.box = "vertical",
  plot.title = element_text(hjust = 0.5, size = 36),
  axis.title = element_text(size = 30),
  axis.text = element_text(size=30)) +
  guides(color = guide_legend(nrow = 5)) +
  scale_y_log10(
    labels = scales::label_number() 
  ) +
  scale_color_manual(values = method_colors)
ggsave(
  filename = "tournament_comparison_plot.png",  # Change file type if needed
  plot = last_plot(),  # Saves the last ggplot created
  dpi = 600,        
  bg = "white",
  units = "in",
  width = 15.28,
  height = 13.43
)

# Apply normalization to all columns except "indices"
df_close <- df_long %>% filter(Method %in% c("Single Elimination (Reseeded)", "Double Elimination", "Group Stage", "Single Elimination (Set Structure)" ))
windowsFonts(Arial = windowsFont("Arial"))
ggplot(df_close, aes(x = indices, y = MI, color = Method, group = Method)) +
geom_line(linewidth = 2.5) +           # Add lines
geom_point(size=3) +          # Add points
labs(
title = "Comparison of Tournament Structures with Normal Strengths",
x = "Top i Number of Teams",
y = "Normalized Mutual Information \\ Entropy (log10 scale)"
) +
theme_minimal() +       # Use a clean theme
theme(text = element_text(family = "Arial", size = 32),
  legend.position = "bottom",
  legend.box = "vertical",
  plot.title = element_text(hjust = 0.5, size = 36),
  axis.title = element_text(size = 30),
  axis.text = element_text(size=30)) +
  guides(color = guide_legend(nrow = 5)) +
  scale_y_log10(
    labels = scales::label_number() 
  ) +
  scale_color_manual(values = method_colors)
ggsave(
  filename = "tournament_comparison_plot_close.png",  # Change file type if needed
  plot = last_plot(),  # Saves the last ggplot created
  dpi = 600,        
  bg = "white",
  units = "in",
  width = 15.28,
  height = 13.43
)

>>>>

# Reshape data into long format for ggplot
df_long <- pivot_longer(mi_plots_df, cols = -indices, names_to = "Method", values_to = "MI")
df_long <- df_long %>% mutate(Method = recode( Method, "Single.Elimination..Reseeded." = "Single Elimination (Reseeded)", "Group.Stage" = "Group Stage", "Double.Elimination" = "Double Elimination", "Single.Elimination..Set.Structure." = "Single Elimination (Set Structure)", "Coin.Flip.Single.Elimination" = "Coin Flip Single Elimination", "Bad.Seeding.Structure.Single.Elimination" = "Bad Seeding Structure Single Elimination", "Coin.Flip.Round.Robin" = "Coin Flip Round Robin", "Round.Robin" = "Round Robin", "Worst.Possible" = "Worst Possible", "Best.Possible" = "Best Possible" ))

okabe_ito <- c(
  "#E69F00", # orange
  "#56B4E9", # sky blue
  "#009E73", # bluish green
  "#F0E442", # yellow
  "#0072B2", # blue
  "#D55E00", # vermillion
  "#CC79A7", # reddish purple
  "#999999", # gray
  "#8A2BE2", # violet (extra)
  "#20B2AA"  # teal (extra)
)
# Compute the ordering of methods by mean MI (descending) 
method_order <- df_long %>% 
  group_by(Method) %>% 
  summarize(mean_MI = mean(MI, na.rm = TRUE)) %>% 
  arrange(desc(mean_MI)) %>% 
  pull(Method)

# Reorder Method factor levels by MI 
df_long <- df_long %>% 
  mutate(Method = factor(Method, levels = method_order))

# Define color mapping in the new order 
methods <- levels(df_long$Method) 
method_colors <- setNames(okabe_ito[seq_along(methods)], methods)

windowsFonts(Arial = windowsFont("Arial"))
comparison_plot <- ggplot(df_long, aes(x = indices, y = MI, color = Method, group = Method)) +
geom_line(linewidth = 2.5) +           # Add lines
geom_point(size=3) +          # Add points
labs(
title = "Comparison of Tournament Structures with Normal Strengths",
x = "Top i Number of Teams",
y = "Normalized Mutual Information \\ Entropy"
) +
theme_minimal() +       # Use a clean theme
theme(text = element_text(family = "Arial", size = 32),
  legend.position = "bottom",
  legend.box = "vertical",
  plot.title = element_text(hjust = 0.5, size = 36),
  axis.title = element_text(size = 30),
  axis.text = element_text(size=30)) +
  guides(color = guide_legend(nrow = 5)) +
  scale_color_manual(values = method_colors)
ggsave(
  filename = "tournament_comparison_plot.png",  # Change file type if needed
  plot = comparison_plot,  # Saves the last ggplot created
  dpi = 600,        
  bg = "white",
  units = "in",
  width = 15.28,
  height = 13.43
)

# Apply normalization to all columns except "indices"
df_close <- df_long %>% filter(Method %in% c("Single Elimination (Reseeded)", "Double Elimination", "Group Stage", "Single Elimination (Set Structure)" ))
windowsFonts(Arial = windowsFont("Arial"))
ggplot(df_close, aes(x = indices, y = MI, color = Method, group = Method)) +
geom_line(linewidth = 2.5) +           # Add lines
geom_point(size=3) +          # Add points
labs(
title = "Comparison of Tournament Structures with Normal Strengths",
x = "Top i Number of Teams",
y = "Normalized Mutual Information \\ Entropy"
) +
theme_minimal() +       # Use a clean theme
theme(text = element_text(family = "Arial", size = 32),
  legend.position = "bottom",
  legend.box = "vertical",
  plot.title = element_text(hjust = 0.5, size = 36),
  axis.title = element_text(size = 30),
  axis.text = element_text(size=30)) +
  guides(color = guide_legend(nrow = 5)) +
  scale_color_manual(values = method_colors)
ggsave(
  filename = "tournament_comparison_plot_close.png",  # Change file type if needed
  plot = last_plot(),  # Saves the last ggplot created
  dpi = 600,        
  bg = "white",
  units = "in",
  width = 15.28,
  height = 13.43
)

### 2025-10-22 single_elimination_shiny.qmd
Updates

  if (distribution == "Normal"){
    strengths <- sapply(num_teams, function(n) { qnorm(1:n/(n+1)) })
    normal_strengths <- data.frame(
      true_rank = as.numeric(teams),
      theta = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA,length(teams)),
      game_wins = rep(0,length(teams)),
      game_losses = rep(0,length(teams))
    )
    df <- arrange(normal_strengths, true_rank)
  }
  else if (distribution == "Same"){
    strengths <- sapply(num_teams, function(n) {rep(0,n)})
    normal_strengths <- data.frame(
      true_rank = as.numeric(teams),
      theta = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA,length(teams)),
      game_wins = rep(0,length(teams)),
      game_losses = rep(0,length(teams))
    )
    df <- arrange(normal_strengths, true_rank)
  }
  else if (distribution == "Uniform"){
    strengths <- sapply(num_teams, function(n) { qunif(1:n/(n+1) , 0 , sqrt(12)) })
    unif_strength <- data.frame(
      true_rank = as.numeric(teams),
      theta = c(strengths, rep(NA, length(teams) - num_teams)),
      game_wins = rep(0,length(teams)),
      game_losses = rep(0,length(teams)),
      rank_hat = rep(NA,length(teams))
    )
    df <- arrange(unif_strength, true_rank)
  }
  else if (distribution == "Manual") {
    cat("Please enter the strengths for each team in descending rank order:\n")
    strengths <- numeric(num_teams)
    for (i in num_teams:1) {
      repeat {
        input <- as.numeric(readline(paste("Strength for Team", num_teams - i + 1, ": ")))
        if (!is.na(input)) {
          strengths[i] <- input
          break
        } else {
          cat("Invalid input. Please enter a numeric value.\n")
        }
      }
    }
    manual_strengths <- data.frame(
      true_rank = as.numeric(teams),
      theta = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA, length(teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams))
    )
    df <- arrange(manual_strengths, true_rank)
  }
  else {
    stop("Distribution not found: Enter Manual to input your own strengths")
  }

@@

  for (i in 1:nrow(seeding_structure)) {
    # Create a new data frame based on the current permutation in 'test'
    permutation <- seeding_structure[i, ]
    permuted_df <- df
    permuted_df$true_rank <- df$true_rank[permutation]  # Update team order 
    teams <- permuted_df$true_rank
    permuted_df$theta <- df$theta[permutation]
    permuted_df$rank_hat <- NA  # Initialize ranks column
    permuted_df$game_wins <- 0  # Initialize wins column
    permuted_df$game_losses <- 0

    strengths <- permuted_df$theta
    round_number <- ceiling(log2(length(teams)))

@@

    # Third place match between the losers of the semifinals
    if (third_place == TRUE){
      team1 <- losers_semis[1]
      team2 <- losers_semis[2]
      strength1 <- permuted_df$theta[permuted_df$true_rank == team1]
      strength2 <- permuted_df$theta[permuted_df$true_rank == team2]
      wins_team1 <- 0
      wins_team2 <- 0
      for (game in 1:series) {
        match_winner <- simulate_match(team1, team2, strength1, strength2)
        if (match_winner == team1) {
          wins_team1 <- wins_team1 + 1
        } else {
          wins_team2 <- wins_team2 + 1
        }
        # Determine the overall winner if a majority is reached
        if (wins_team1 > series / 2 || wins_team2 > series / 2) {
          break
        }
      }
      # Assign third place and fourth place ranks
      if (wins_team1 > wins_team2) {
        #cat(sprintf("Third Place Matchup: %s vs %s | Winner: %s\n", team1, team2, team1))
        permuted_df$rank_hat[permuted_df$true_rank == team1] <- 3
        permuted_df$rank_hat[permuted_df$true_rank == team2] <- 4
      } else {
        #cat(sprintf("Third Place Matchup: %s vs %s | Winner: %s\n", team1, team2, team2))
        permuted_df$rank_hat[permuted_df$true_rank == team2] <- 3
        permuted_df$rank_hat[permuted_df$true_rank == team1] <- 4
      }
    }

@@

test <- simulate_single_elimination_tournament(num_teams = 8, distribution = "Same", ties=F, series=1, third_place=T, seeding_structure = c(1,2,3,4,5,6,7,8), reseeded = TRUE)
test

@@

# Gets all results of a normal distribution num_teams between 4 and 64 single-game elimination
all_normal_results <- list()
for (teams in c(8)) {
  all_normal_results[[as.character(teams)]] <- list()
  for (replicate in 1:10000) {
    # Store each simulation result in the list with unique indexing
    all_normal_results[[as.character(teams)]][[replicate]] <- simulate_single_elimination_tournament(
      num_teams = teams,
      distribution = "Normal",
      ties = FALSE,
      series = 1,
      third_place = FALSE
    )
  }
}

>>>>

  if (distribution == "Normal"){
    strengths <- sapply(num_teams, function(n) { qnorm(1:n/(n+1)) })
    normal_strengths <- data.frame(
      true_rank = as.numeric(teams),
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA,length(teams)),
      game_wins = rep(0,length(teams)),
      game_losses = rep(0,length(teams))
    )
    df <- arrange(normal_strengths, true_rank)
  }
  else if (distribution == "Same"){
    strengths <- sapply(num_teams, function(n) {rep(0,n)})
    normal_strengths <- data.frame(
      true_rank = as.numeric(teams),
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA,length(teams)),
      game_wins = rep(0,length(teams)),
      game_losses = rep(0,length(teams))
    )
    df <- arrange(normal_strengths, true_rank)
  }
  else if (distribution == "Uniform"){
    strengths <- sapply(num_teams, function(n) { qunif(1:n/(n+1) , 0 , sqrt(12)) })
    unif_strength <- data.frame(
      true_rank = as.numeric(teams),
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      game_wins = rep(0,length(teams)),
      game_losses = rep(0,length(teams)),
      rank_hat = rep(NA,length(teams))
    )
    df <- arrange(unif_strength, true_rank)
  }
  else if (distribution == "Manual") {
    cat("Please enter the strengths for each team in descending rank order:\n")
    strengths <- numeric(num_teams)
    for (i in num_teams:1) {
      repeat {
        input <- as.numeric(readline(paste("Strength for Team", num_teams - i + 1, ": ")))
        if (!is.na(input)) {
          strengths[i] <- input
          break
        } else {
          cat("Invalid input. Please enter a numeric value.\n")
        }
      }
    }
    manual_strengths <- data.frame(
      true_rank = as.numeric(teams),
      true_strength = c(strengths, rep(NA, length(teams) - num_teams)),
      rank_hat = rep(NA, length(teams)),
      game_wins = rep(0, length(teams)),
      game_losses = rep(0, length(teams))
    )
    df <- arrange(manual_strengths, true_rank)
  }
  else {
    stop("Distribution not found: Enter Manual to input your own strengths")
  }

@@

  for (i in 1:nrow(seeding_structure)) {
    # Create a new data frame based on the current permutation in 'test'
    permutation <- seeding_structure[i, ]
    permuted_df <- df
    permuted_df$true_rank <- df$true_rank[permutation]  # Update team order 
    teams <- permuted_df$true_rank
    permuted_df$true_strength <- df$true_strength[permutation]
    permuted_df$rank_hat <- NA  # Initialize ranks column
    permuted_df$game_wins <- 0  # Initialize wins column
    permuted_df$game_losses <- 0

    strengths <- permuted_df$true_strength
    round_number <- ceiling(log2(length(teams)))

@@

    # Third place match between the losers of the semifinals
    if (third_place == TRUE){
      team1 <- losers_semis[1]
      team2 <- losers_semis[2]
      strength1 <- permuted_df$true_strength[permuted_df$true_rank == team1]
      strength2 <- permuted_df$true_strength[permuted_df$true_rank == team2]
      wins_team1 <- 0
      wins_team2 <- 0
      losses_team1 <- 0
      losses_team2 <- 0
      for (game in 1:series) {
        match_winner <- simulate_match(team1, team2, strength1, strength2)
        if (match_winner == team1) {
          wins_team1 <- wins_team1 + 1
          losses_team2 <- losses_team2 + 1

        } else {
          wins_team2 <- wins_team2 + 1
          losses_team1 <- losses_team1 + 1
        }
        # Determine the overall winner if a majority is reached
        if (wins_team1 > series / 2 || wins_team2 > series / 2) {
          break
        }
      }

      # Update game_wins / game_losses in permuted_df for both teams
        permuted_df <- permuted_df %>%
          mutate(game_wins = ifelse(true_rank == team1, game_wins + wins_team1, game_wins)) %>%
          mutate(game_wins = ifelse(true_rank == team2, game_wins + wins_team2, game_wins)) %>%
          mutate(game_losses = ifelse(true_rank == team1, game_losses + losses_team1, game_losses)) %>%
          mutate(game_losses = ifelse(true_rank == team2, game_losses + losses_team2, game_losses))

      # Assign third place and fourth place ranks
      if (wins_team1 > wins_team2) {
        #cat(sprintf("Third Place Matchup: %s vs %s | Winner: %s\n", team1, team2, team1))
        permuted_df$rank_hat[permuted_df$true_rank == team1] <- 3
        permuted_df$rank_hat[permuted_df$true_rank == team2] <- 4
      } else {
        #cat(sprintf("Third Place Matchup: %s vs %s | Winner: %s\n", team1, team2, team2))
        permuted_df$rank_hat[permuted_df$true_rank == team2] <- 3
        permuted_df$rank_hat[permuted_df$true_rank == team1] <- 4
      }
    }

@@

single_run_example <- simulate_single_elimination_tournament(num_teams = 8, distribution = "Normal", ties=F, series=1, third_place=T, reseeded=F)

@@

# Gets all results of a normal distribution num_teams between 4 and 64 single-game elimination
all_normal_results <- list()
for (teams in c(8)) {
  all_normal_results[[as.character(teams)]] <- list()
  for (replicate in 1:10000) {
    # Store each simulation result in the list with unique indexing
    all_normal_results[[as.character(teams)]][[replicate]] <- simulate_single_elimination_tournament(
      num_teams = teams,
      distribution = "Normal",
      ties = FALSE,
      series = 1,
      third_place = TRUE
    )
  }
}
